An iterated Grothendieck construction of semi-cubical types

### 2022-02-23 paper/paper.tex
_CoqProject: add a stub for VSCoq

% Type theory
\newcommand{\UU}{\ensuremath{\mathscr{U}}}

@@

  \begin{align*}
    d_i d_j & = d_{j - 1} d_i, i < j \\
    s_i s_j & = s_{j + 1} s_i, i < j \\
    d_i s_j & =
    \begin{cases}
      s_{j - 1} d_i & i < j \\
      id            & i = j \\
      s_j d_{i - 1} & i > j \\
    \end{cases}
  \end{align*}
\end{definition}

@@

$$
  \begin{tikzcd}
    X_0 : \UU & X_1 : \UU \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \UU \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
  \end{tikzcd}
$$

\begin{align*}
  X_0 & : \UU                                                                                                      \\
  X_1 & : X_0 \times X_0 \rightarrow \UU                                                                           \\
  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \UU \\
  \ldots
\end{align*}

>>>>

@@

  \begin{equation*}
    \begin{matrix}
      d_i d_j & = & d_{j - 1} d_i & i < j \\
      s_i s_j & = & s_{j + 1} s_i & i < j \\
      d_i s_j & = &
      \begin{cases}
        s_{j - 1} d_i & i < j \\
        id            & i = j \\
        s_j d_{i - 1} & i > j \\
      \end{cases}
    \end{matrix}
  \end{equation*}
\end{definition}

@@

$$
  \begin{tikzcd}
    X_0 : \sort{} & X_1 : \sort{} \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] & X_2 : \sort{} \arrow[l, "\delta^\epsilon_1" description, shift left=6] \arrow[l, "\delta^\epsilon_0" description, shift left=2] \arrow[l, "\delta^\omega_0" description, shift right=2] \arrow[l, "\delta^\omega_1" description, shift right=6] & \ldots
  \end{tikzcd}
$$

\begin{align*}
  X_0 & : \sort{}                                                                                                      \\
  X_1 & : X_0 \times X_0 \rightarrow \sort{}                                                                           \\
  X_2 & : \forall a b c d, X_1 : ab \rightarrow X_1 : bc \rightarrow X_1 : cd \rightarrow X_1 : da \rightarrow \sort{} \\
  \ldots
\end{align*}
